### 2015-06-07 doc/manual/resolution.tex
Now displaying spread percentages in sfincsScanPlot_1

Typical convergence behavior is illustrated in figure \ref{fig:convergence},
showing the results of \sfincsScan~and \sfincsScanPlot~for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
In this figure, a very large number of runs are included in the scan,
more than you would likely include in routine use of the code.
The red vertical lines emphasize the ``base case'' resolution parameters.
For all parameters scanned, the physical output quantities (particle flux, heat flux, etc)
do not visibly change (on the scale of the plots) when any of the resolution parameters
are increased beyond the base case value.  Thus, the results in the base case are well converged,
and so we can believe the results.
Observe in the figure that the output quantities tend to oscillate when \Nxi~is incremented by 1 and insufficient
\Nxi~is used. Results for even and odd \Nxi~converge to the same value, as one would hope.

@@

For routine use of the code, it is not necessary to include as many
runs in the convergence scan as shown in figure \ref{fig:convergence},
and so a more typical routine scan would look like figure \ref{fig:convergence2}.
This scan is for a pure hydrogen plasma in the W7-X standard configuration, using \parlink{rN} = 0.19,
$n_e$ = $10^{20}$ m$^{-3}$, $T_i$ = 3.6 keV, and $T_e$ = 5.5 keV.
Notice the vertical scales in figure \ref{fig:convergence2} have suppressed zeros.
For all of the physical output quantities, the results change by no more than a few percent when each resolution
parameter is increased by 50\%. Hence we can conclude that 
the results are suitably converged at the base case resolution parameters.
The \sfincs~resolution parameters and \sfincsScan~parameters used for this scan were as follows:\\
{\ttfamily
\Ntheta = 19 \\
!ss \parlink{NthetaMinFactor} = 0.7 \\
!ss \parlink{NthetaMaxFactor} = 1.5 \\
!ss \parlink{NthetaNumRuns} = 6 \\
\Nzeta = 125 \\
!ss \parlink{NzetaMinFactor} = 0.7 \\
!ss \parlink{NzetaMaxFactor} = 1.5 \\
!ss \parlink{NzetaNumRuns} = 8 \\
\Nxi = 140 \\
!ss \parlink{NxiMinFactor} = 0.7 \\
!ss \parlink{NxiMaxFactor} = 1.5 \\
!ss \parlink{NxiNumRuns} = 8 \\
\Nx = 5 \\
!ss \parlink{NxMinFactor} = 1 \\
!ss \parlink{NxMaxFactor} = 1.6 \\
!ss \parlink{NxNumRuns} = 4 \\
}
These \sfincsScan~parameters are good for routine convergence tests, although the \sfincs~parameters proper
(\Ntheta, \Nzeta, \Nxi, and \Nx) should be tailored to your application.

>>>>

Typical convergence behavior is illustrated in figure \ref{fig:convergence},
showing the results of \sfincsScan~and \sfincsScanPlot~for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
In this figure, a very large number of runs are included in the scan,
more than you would likely include in routine use of the code.
The red vertical lines emphasize the ``base case'' resolution parameters.
In each figure the spread is printed, defined as the maximum value $-$ minimum value,
divided by the value half-way between maximum and minimum.
If some runs have resolution below the base resolution,
the spread is also computed and printed
excluding runs below the base case resolution. (This is the second percentage printed in each plot,
and is usually more important than the first spread percentage.)
For all parameters scanned, the physical output quantities (particle flux, heat flux, etc)
do not visibly change on the scale of the plots when any of the resolution parameters
are increased beyond the base case value.  Indeed, the spread for each output quantity is $\le$ 3.5\%
when any resolution parameter is increased.
Thus, the results in the base case are well converged,
and so we can believe the results.
Observe in the figure that the output quantities tend to oscillate when \Nxi~is incremented by 1 and insufficient
\Nxi~is used. Results for even and odd \Nxi~converge to the same value, as one would hope.

@@

For routine use of the code, it is not necessary to include as many
runs in the convergence scan as shown in figure \ref{fig:convergence},
and so a more typical routine scan would look like figure \ref{fig:convergence2}.
This scan is for a pure hydrogen plasma in the W7-X standard configuration, using \parlink{rN} = 0.19,
$n_e$ = $10^{20}$ m$^{-3}$, $T_i$ = 3.6 keV, and $T_e$ = 5.5 keV.
Notice the vertical scales in figure \ref{fig:convergence2} have suppressed zeros.
For all of the physical output quantities, the spread beyond the base case is $\le$ 3.4\%,
i.e. results change by no more than this percentage when each resolution
parameter is increased by 50\%. Hence we can conclude that 
the results are suitably converged at the base case resolution parameters.
The \sfincs~resolution parameters and \sfincsScan~parameters used for this scan were as follows:\\
{\ttfamily
\Ntheta = 19 \\
!ss \parlink{NthetaMinFactor} = 0.7 \\
!ss \parlink{NthetaMaxFactor} = 1.5 \\
!ss \parlink{NthetaNumRuns} = 6 \\
\Nzeta = 125 \\
!ss \parlink{NzetaMinFactor} = 0.7 \\
!ss \parlink{NzetaMaxFactor} = 1.5 \\
!ss \parlink{NzetaNumRuns} = 8 \\
\Nxi = 140 \\
!ss \parlink{NxiMinFactor} = 0.7 \\
!ss \parlink{NxiMaxFactor} = 1.5 \\
!ss \parlink{NxiNumRuns} = 8 \\
\Nx = 5 \\
!ss \parlink{NxMinFactor} = 1 \\
!ss \parlink{NxMaxFactor} = 1.6 \\
!ss \parlink{NxNumRuns} = 4 \\
}
These \sfincsScan~parameters are good for routine convergence tests, although the \sfincs~parameters proper
(\Ntheta, \Nzeta, \Nxi, and \Nx) should be tailored to your application.
